Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-15 ICML2019/main.tex
pass on absrtract

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space of differentially private Bayesian
inference mechanisms with accuracy measured in terms of Hellinger
distance over posterior distributtions.  
We focus on two discrete models for parametric Bayesian
inference: the Beta-Binomial and the Dirichlet-Multinomial
models. We study two mechanisms based on the 
Laplace perturbation of the parameters of the posterior distribution under
$\ell_1$ norm, and compare them with variations of the exponential
mechanism calibrated to Hellinger distance. We
measure the accuracy using the Hellinger distance between the posterior
distribution released by the different mechanisms and the real one.
We compare the accuracy theoretically and experimentally.
\end{abstract}
 % TODO: replace with your keywords

>>>>

\begin{abstract}
% Several approaches have been explored in order to make Bayesian inference
% differentially private.
% For instance, \cite{dimitrakakis2014robust} and
% \cite{wang2015privacy} proved that, under specific conditions of the likelihood function and the prior distribution,
% sampling from the posterior distribution, is already differentially private. \cite{zhang2016differential} and \cite{foulds2016theory}
% designed differentially private (d.p.) mechanisms by adding laplacian noise
% to the numeric parameters of the posterior distributions. 
% Accuracy, is usally (\cite{??}) measured by providing upper bounds, holding w.h.p, on the
% $\ell_1$ or $\ell_\infty$-distance between the numeric parameters
% of the released posterior distribution and the actual real ones of posterior distribution.
We explore the design space of differentially private Bayesian
inference mechanisms with accuracy measured in terms of Hellinger
distance over posterior distributions.  
We focus on two discrete models for parametric Bayesian
inference: the Beta-Binomial and the Dirichlet-Multinomial
models. We study two mechanisms based on the 
Laplace perturbation of the parameters of the posterior distribution under
$\ell_1$ norm, and compare them with variations of the Exponential
mechanism where the score function is based on the Hellinger distance.
Accuracy is measured through the Hellinger distance between the posterior
distribution released by the different mechanisms and the real one.
We compare the accuracy theoretically and experimentally.
\end{abstract}
 % TODO: replace with your keywords
